MaxEnt: What is it good for?

### 2015-06-18 ms.tex
Giffin!

\section*{Acknowledgements}
It is a pleasure to thank
Ariel Caticha (Albany),
John Skilling (MaxEnt Data Consultants),
Carlos Rodriguez (),
Stephen Gull (),
Kevin Knuth (Albany),
Iain Murray (Edinburgh),
Anna Pancoast (UCSB),
Geraint Lewis (Sydney),
David Hogg (NYU),
Tom Loredo (Cornell),
Daniela Huppenkothen (NYU),
Peter Tuthill (Sydney),

>>>>

\section*{Acknowledgements}
It is a pleasure to thank
Ariel Caticha (Albany),
Adom Giffin (Clarkson)
John Skilling (MaxEnt Data Consultants),
Carlos Rodriguez (Albany),
Stephen Gull (Cambridge),
Kevin Knuth (Albany),
Iain Murray (Edinburgh),
Anna Pancoast (UCSB),
Geraint Lewis (Sydney),
David Hogg (NYU),
Tom Loredo (Cornell),
Daniela Huppenkothen (NYU),
Peter Tuthill (Sydney),
